---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# weightdictR

<!-- badges: start -->
<!-- badges: end -->

The goal of weightdictR is to facialiate the deployment of weighted dictionaries especially one including complex muliword pattern.

## Installation

You can install the development version of weightdictR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("TomSOWI/weightdictR")
```

## Example

First of all clean and prepare textdata. This is **only necessary** if the weighted dictionary includes **complex multiword-patterns**.

```{r example}

devtools::install_github("TomSOWI/weightdictR")

library(weightdictR)
library(quanteda)
library(dplyr)


#First of all clean and prepare textdata. This is only necessary if the weighted dictionary includes complex multiword-patterns.

toksBT17_20_clean <- corpus_to_compound_tokens(corpus = corpBT17_20,
  pattern = klotz_clara$pattern,
  include_totals = TRUE)

#Include party variable
quanteda::docvars(toksBT17_20_clean)$party <- docvars(corpBT17_20)$party


#This is already done for the example
weightdictR::toksBT17_20_clean

#This is my dictionary
weightdictR::klotz_clara


#Deploy my weighted dictionary using the main function of this package: **run_weightdict**

result_klotz <- run_weightdict(
  text = weightdictR::toksBT17_20_clean,
  dict = klotz_clara,
  dict_name = "klotz"
  )

# Individual context information -----------------------------------------------

#Add party 
party <- data.frame(docname = quanteda::docnames(corpBT17_20), party = docvars(corpBT17_20)$party)
result_klotz <- merge(result_klotz, party)

#Add totals
totals <- data.frame(docname = quanteda::docnames(corpBT17_20), nsentences = nsentence(corpBT17_20), ntokens = ntoken(corpBT17_20))
result_klotz <- merge(result_klotz, totals)

# Final result
result <- result_klotz %>%
  group_by(party) %>%
  reframe(
    nsentence = sum(nsentences),
    ntokens = sum(ntokens),
    klotz_clara = sum(weight)/nsentence,
  )
result

#You may continue by comparing the results using z-transformation
result$klotz_clara_z <- scale(result$klotz_clara, center = T)

```


